Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-04 inc/hardware/column.tex
merge comments on column

Apart from the laser system, the majority of an Ultrafast Electron Microscope column is either vacuum hardware or contained within the vacuum system.
The vacuum chamber itself is almost entirely 4.5 in standard ConFlat hardware.
Much has been purchased from off-the-shelf hardware suppliers.
Some of the more specialized chamber components have been fabricated in-house or purchased from Kimball Physics Inc.

@@

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube,'' a large stainless-steel sphere which has six 4.5 in ConFlat ports oriented as a cube, with another eight 1.33 in ports on the corners of the cube.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''
This system is used to mount the accelerator anode and the the deflector plates which are both to be described later.

>>>>

Apart from the laser system, the majority of an Ultrafast Electron Microscope column is either vacuum hardware or contained within the vacuum system.
The vacuum chamber itself is almost entirely standard 4.5 in ConFlat (CF) hardware.
Much has been purchased from off-the-shelf hardware suppliers.
Some of the more specialized chamber components have been fabricated in-house or purchased from Kimball Physics Inc.

@@

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube''; a large stainless-steel sphere which has six 4.5 in ConFlat ports oriented as a cube, with another eight 1.33 in ports on the corners of the cube.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''
This system is used to mount the accelerator anode and the deflector plates which are both to be described later.
